A Survey of Scientific Workflow Management Systems

### 2014-04-15 paper.tex
double space
comments
new fig and desc

@@

@@

In this work we conduct a literature study of the key features of the
contemporary scientific workflow environments. The criteria for study are
defined. An overview of studied scientific workflow environments is given
followed by the identification and description of the features offered by each
of the environment. A tabulated summary for each feature gives a high-level
view of the offered features. Finally, a taxonomy is proposed placing these
features into respective places in a hierarchy.

@@

\section{Architecture of a Generic SWE}
Figure \ref{fig:wfms} shows a high-level architecture of a SWE. It shows key
components and their interaction in a SWE. These components are the focus of
interest for the present work. A \textit{user interface} interacts with the
\textit{workflow engine} using commands and messages. The \textit{workflow
language} becomes an intermediate representation for communication between user
interface and the \textit{workflow engine}. The workflow engine acts as a
compiler/interpreter and scheduler for the workflow tasks and interfaces with
the underlying \textit{distributed resources}. It also monitors the workflow
progress and collects the intermediate and final results.

>>>>

\usepackage{setspace}
%\doublespacing
\linespread{2}

@@

\newcommand{\jm}[1]{
    \noindent{\textcolor{red}{\bf\em #1 -- Johan}}
}
\newcommand{\km}[1]{
    \noindent{\textcolor{blue}{\bf\em #1 -- Ketan}}
}

@@

\km{TODO: Expand in the end}

In this work we conduct a literature survey of the key features of the
contemporary scientific workflow environments. We define the criteria for the
survey based chiefly on user needs arising from diverse applications and
infrastructure. An overview of studied scientific workflow environments is
presented followed by the identification and description of the features offered by
each of the environment. A tabulated summary for each feature class gives a
high-level view of the offered features. Finally, a taxonomy is proposed
placing these features into respective places in a hierarchy.

\jm{Test comment}

@@

\section{Conceptual Overview}
In this section we present a conceptual overview of the subjects of this study--Workflows and Scientific Workflow Environments.

\subsection{Workflow}
Figure~\ref{fig:wf} shows a typical workflow in the form of a Directed Acyclic
Graph (DAG). For the purpose of this text, we define a workflow as a
computation with at least two discrete tasks either forming distinct
computational stages or running for two or more distinct datasets as
parameters. Consequently, a one-off task or running a task for a single copy of
data is \emph{not} a workflow. For the rest of this paper, we will use the above
definition of a workflow.
%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=4cm]{figures/workflow}
\caption{A typical workflow depicted as a Directed Acyclic Graph (DAG) of tasks coordinated by data or control flow and illustrating data and task parallelism}
\label{fig:wf}
\end{center}
\end{figure}
%
\subsection{Architecture of a Generic SWE}
Figure~\ref{fig:wfms} shows a high-level architecture of a SWE. It shows key
components and their interaction in a SWE. These components are the focus of
interest for the present work. A \textit{user interface} interacts with the
\textit{workflow engine} using commands and messages. The \textit{workflow
language} becomes an intermediate representation for communication between user
interface and the \textit{workflow engine}. The workflow engine acts as a
compiler/interpreter and scheduler for the workflow tasks and interfaces with
the underlying \textit{distributed resources}. It also monitors the workflow
progress and collects the intermediate and final results.
